Assignment 3

### 2019-07-31 ex3/report/report.tex
Added per-family table

The method minimizes the adversarial sample's distance so that the network's decision is just between attack and normal traffic. In the present context, we

@@

@@

>>>>

The method minimizes the adversarial sample's distance so that the network's decision is just between attack and normal traffic. In the present context, we need to make sure that the classifer's prediction would actually be normal traffic, even though a certain level of noise will be added to interarrival times due to the network between attacker and victim. Instead of the above equation \ref{eq:carliniWagner} we therefore used the optimization objective
\begin{equation} \label{eq:carliniWagner}
d(X,\tilde X) + \epsilon  \max(Z(\tilde X), -0.2),
\end{equation}
i.e. we require a slight level of confidence that our adversarial samples are not classified as attack traffic.

@@

\autoref{tab:adv_per_family} depicts how successful the attack is for individual attack families. For this table we used a $\ell_\infty$ bound of 0.3 for FGSM and $\ell_\infty$-bounded PGD and a tradeoff of 0.5 for Carlini-Wagner. The table shows significant for detecting different attack families in the first place. However, also for generating adversarial flows some attack families are more susceptible than others.

@@

Finally, we investigated how adversarial flows look like and which features are manipulated to circumvent detection by the neural network.

To this end, we generated adversarial flows with the Carlini-Wagner method with $\ell_2$ distance and a tradeoff of 0.5. \autoref{adv_plots} depicts how the method manipulates flows for some exemplary attack categories.

\begin{figure*}
\includegraphics[width=0.48\textwidth]{../plots/plot_adv/1.pdf}
\includegraphics[width=0.48\textwidth]{../plots/plot_adv/2.pdf}
\includegraphics[width=0.48\textwidth]{../plots/plot_adv/3.pdf}
\includegraphics[width=0.48\textwidth]{../plots/plot_adv/4.pdf}
\caption{Successful manipulations performed by the Carlini-Wagner method.}
\label{adv_plots}
\end{figure*}

\begin{table*}
\caption{Attack success ratios per attack family. Depicted are flow detection accuracies for adversarial flows (left numbers) and flow detection accuracies for unmodified flows (right numbers).}
\label{tab:adv_per_family}
\begin{tabular}{lllllllll} 
\toprule
Attack type & FGSM & Carlini-Wagner, $\ell_1$ & Carlini-Wagner, $\ell_2$ & $\ell_\infty$-bounded PGD \\
\midrule
Botnet:ARES	&	0.0000 / 0.0000	&	0.0000 / 0.0000	&	0.0000 / 0.0000	&	0.0000 / 0.0000	\\
Brute Force:FTP-Patator	&	0.2800 / 0.5800	&	0.1600 / 0.5800	&	0.1600 / 0.5800	&	0.2800 / 0.5800	\\
Brute Force:SSH-Patator	&	0.8300 / 1.0000	&	0.0000 / 1.0000	&	0.0000 / 1.0000	&	0.8900 / 1.0000	\\
DDoS:LOIT	&	0.8300 / 0.8600	&	0.6400 / 0.8600	&	0.5600 / 0.8600	&	0.8200 / 0.8600	\\
DoS / DDoS:DoS GoldenEye	&	0.8900 / 1.0000	&	0.5000 / 1.0000	&	0.4200 / 1.0000	&	0.9200 / 1.0000	\\
DoS / DDoS:DoS Hulk	&	0.6700 / 1.0000	&	0.5400 / 1.0000	&	0.4700 / 1.0000	&	1.0000 / 1.0000	\\
DoS / DDoS:DoS Slowhttptest	&	0.8700 / 1.0000	&	0.4100 / 1.0000	&	0.1900 / 1.0000	&	0.7400 / 1.0000	\\
DoS / DDoS:DoS slowloris	&	0.4400 / 0.9700	&	0.3100 / 0.9700	&	0.1300 / 0.9700	&	0.9200 / 0.9700	\\
DoS / DDoS:Heartbleed	&	0.0000 / 0.0000	&	0.0000 / 0.0000	&	0.0000 / 0.0000	&	0.0000 / 0.0000	\\
Infiltration:Dropbox download 	&	0.6100 / 0.9600	&	0.4300 / 0.9600	&	0.3800 / 0.9600	&	0.7400 / 0.9600	\\
PortScan:PortScan - Firewall off	&	0.6800 / 0.9100	&	0.3500 / 0.9100	&	0.3500 / 0.9100	&	0.7200 / 0.9100	\\
PortScan:PortScan - Firewall on	&	0.7400 / 0.8700	&	0.6100 / 0.8700	&	0.5300 / 0.8700	&	0.7300 / 0.8700	\\
Web Attack:Sql Injection	&	0.0000 / 0.6923	&	0.0000 / 0.6923	&	0.0000 / 0.6923	&	0.0000 / 0.6923	\\
Web Attack:XSS	&	0.6700 / 0.9500	&	0.7200 / 0.9500	&	0.6200 / 0.9500	&	0.6700 / 0.9500	\\
\bottomrule

\end{tabular}
\end{table*}
